### 2016-09-09 doc/manual/version3/inputParameters.tex

>>>>

\param{Nxi\_for\_x\_option}
{integer}
{1}
{Always}
{This setting controls how the number of Legendre polynomials depends on the speed $x$ for representing the distribution function.
You can see the actual number of Legendre polynomials used for each $x$ grid point by examining the {\ttfamily Nxi\_for\_x} variable
in the output file.\\

{\ttfamily Nxi\_for\_x\_option} = 0: Use the same number (\parlink{Nxi}) of Legendre polynomials for all $x$.  This approach is
simplest, but it is somewhat inefficient since small values of $x$ represent higher collisionality, so there is weaker pitch-angle dependence
of the distribution function.\\

{\ttfamily Nxi\_for\_x\_option} = 1: The number of Legendre polynomials will be a linear function of $x$ up to $x=2$,
at which point \parlink{Nxi} polynomials will be used. For $x>2$, the number of Legendre polynomials used will remain at \parlink{Nxi}.\\

{\ttfamily Nxi\_for\_x\_option} = 2: The number of Legendre polynomials will be a quadratic function of $x$ up to $x=2$,
at which point \parlink{Nxi} polynomials will be used. For $x>2$, the number of Legendre polynomials used will remain at \parlink{Nxi}.\\

}
